### 2020-07-20 paper/conclusion.tex
After Andrei's comments
Cover letter and minor changes

The insertion of CRs deforms the radial flux shape in certain positions, i.e., around CRs. This shifts the neutron flux from the core center towards the periphery.

@@

\section{Future work}
In Part II of this research effort, we will evaluate the effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using a
SERPENT-2 online reprocessing subroutine and 
batch-wise tool SaltProc \cite{rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, a multi-physics application for liquid-fueled MSR 
simulation which takes into account the neutron precursors drift.

>>>>

The insertion of CRs deforms the radial flux shape close to CRs. This shifts the neutron flux from the core center towards the periphery.

@@

\section{Future work}
The authors intend to evaluate the effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using a
SERPENT-2 online reprocessing subroutine and 
batch-wise tool SaltProc \cite{rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, a multi-physics application for liquid-fueled MSR 
simulation which takes into account the neutron precursors drift.

### 2020-07-20 paper/cover-letter/cover-letter.tex
Cover letter and minor changes

\documentclass[10.75pt]{letter} % Default font size of the document, change to 10pt to fit more text
\usepackage{graphicx}
%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

@@

%--------------------------------------------------------------------------------------
%--------INPUT DATA
%--------------------------------------------------------------------------------------
\usepackage{xspace}
\newcommand{\StudentFirstName}{O.\xspace}
\newcommand{\StudentLastName}{Ashraf\xspace}
\newcommand{\RecipientName}{Profs. Azmy, Joyce, and Su\xspace}
\newcommand{\RecipientAddress}{Executive Editor\\Progress in Nuclear Energy}
%\newcommand{\<++>}{<++>\xspace}

@@

		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR). Part I: Design development, material selection, and worth analysis'' which I and my coauthors (Mr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, and Prof. Kathryn D. Huff) are submitting for exclusive consideration of publication as a research article in Progress in Nuclear Energy. The current manuscript is the first part of the two-part series that introduces a reliable safety system based on control rods in addition to the online feed system reactivity control in the SD-TMSR. Part I focus on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady state. Meanwhile, Part II will focus on control rod worth evolution during operation. We intended to submit Part II on June-July, 2020.

@@

		Thank you for your consideration of our work. I expect it will be of interest
		to a broad readership concerned with simulation of MSRs.\\

@@

		\closing{Sincere regards,
			\includegraphics[height=1.3cm]{signature.png}\\
			\fromsig{O. Ashraf\\
				Assistant Teacher\\
				Institute of Nuc. Physics and Eng.\\
				National Research Nuclear University (MEPhI)}
		}

>>>>

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
\usepackage{graphicx}
%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

@@

%--------------------------------------------------------------------------------------
%--------INPUT DATA
%--------------------------------------------------------------------------------------
\usepackage{xspace}
\newcommand{\StudentFirstName}{O.\xspace}
\newcommand{\StudentLastName}{Ashraf\xspace}
\newcommand{\RecipientName}{Prof. Mostafa Ghiaasiaan\xspace}
\newcommand{\RecipientAddress}{Executive Editor\\Annals of Nuclear Energy}
%\newcommand{\<++>}{<++>\xspace}

@@

		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)'' which I and my coauthors (Mr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, and Prof. Kathryn D. Huff) are submitting for exclusive consideration of publication as a research article in Annals of Nuclear Energy. The current manuscript introduces a reliable safety system based on control rods in addition to the online feed system reactivity control in the SD-TMSR. This paper focuses on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady state.

		Notably, this paper in its initial form has been rejected from Progress of Nuclear Energy journal. However, we have addressed the major concerns of the reviewers. It is our belief that the manuscript is substantially improved after implementing the suggested comments and edits.

@@

		Thank you for your consideration of our work. We expect it will be of interest
		to a broad readership concerned with simulation of MSRs.\\

@@

		\closing{Sincere regards,
	\includegraphics[height=1.5cm]{signature.png}\\
	\fromsig{O. Ashraf\\
		Assistant Teacher\\
		Institute of Nuc. Physics and Eng.\\
		National Research Nuclear University (MEPhI)}
}
